Solution of hydrodynamic equilibrium in black-oil reservoirs: the classical material balance equation

### 2014-09-22 pituba/article/article_spe.tex
fixed compaction of porous volume

\begin{table*}
\small
\centering
\begin{tabular}{ll}
\toprule
\multicolumn{2}{l}{\textit{Material balance equation}}\\
\midrule
pressure & $F_p - F_i= N E_o + mN E_g + W E_w +C$ \\
\midrule
\multicolumn{2}{l}{\textit{Phase saturations}}\\
\midrule
oil & $S_{o2} = \left(N-N_p\right) B_{o2}/V_{p2}$ \label{eq: oiltab}
\\
water & $S_{w2} = \left(W+W_i+W_e-W_p\right) B_{w2}/V_{p2}$\\
gas & $S_{g2}=\left\lbrace N\left[\left(R_{s1}-R_{s2}\right)+m B_{o1}/B_{g1}\right]+N_p R_{s2}+G_i-G_p\right\rbrace Bg_2/V_{p2}$ \\
\midrule
\multicolumn{2}{l}{\textit{List of terms}} \\
\midrule
fluid production & $F_p=N_p \left[B_{o2} + \left(G_p/N_p -R_{s2}\right)B_{g2}\right]+W_p B_{w2}$ \\
fluid injection and influx & $F_i=\left(W_i +W_e\right) B_{w2}+G_{i}B_{g2}$ \\
fluid expansion & $E=N E_o + mN E_g + W E_w$ \\
oil phase expansion & $E_o=\left(B_{o2}-B_{o1}\right) - \left(R_{so2}-R_{so1}\right)B_{g2}$ \\
gas phase expansion & $E_g = B_{o1}\left(B_{g2}/B_{g1}-1\right)$ \\
water volume expansion & $E_w = B_{w2}-B_{w1}$\\
porous volume contraction & $C=V_{p2}- V_{p1}$\\
bubble-point pressure & $R_{s2}\left(P_b\right) = \left[N\left(m B_{1}/B_{g1} +R_{s1}\right)+G_i-G_p\right]/\left(N-N_p\right)$ \\ \bottomrule
\end{tabular}
\caption{Complete set of material balance equations.}
\label{tab: MBE}
\end{table*}

>>>>

\begin{table*}
\small
\centering
\begin{tabular}{ll}
\toprule
\multicolumn{2}{l}{\textit{Material balance equation}}\\
\midrule
pressure & $F_p - F_i= N E_o + mN E_g + W E_w +C$ \\
\midrule
\multicolumn{2}{l}{\textit{Phase saturations}}\\
\midrule
oil & $S_{o2} = \left(N-N_p\right) B_{o2}/V_{p2}$ \label{eq: oiltab}
\\
water & $S_{w2} = \left(W+W_i+W_e-W_p\right) B_{w2}/V_{p2}$\\
gas & $S_{g2}=\left\lbrace N\left[\left(R_{s1}-R_{s2}\right)+m B_{o1}/B_{g1}\right]+N_p R_{s2}+G_i-G_p\right\rbrace Bg_2/V_{p2}$ \\
\midrule
\multicolumn{2}{l}{\textit{List of terms}} \\
\midrule
fluid production & $F_p=N_p \left[B_{o2} + \left(G_p/N_p -R_{s2}\right)B_{g2}\right]+W_p B_{w2}$ \\
fluid injection and influx & $F_i=\left(W_i +W_e\right) B_{w2}+G_{i}B_{g2}$ \\
fluid expansion & $E=N E_o + mN E_g + W E_w$ \\
oil phase expansion & $E_o=\left(B_{o2}-B_{o1}\right) - \left(R_{so2}-R_{so1}\right)B_{g2}$ \\
gas phase expansion & $E_g = B_{o1}\left(B_{g2}/B_{g1}-1\right)$ \\
water volume expansion & $E_w = B_{w2}-B_{w1}$\\
porous volume contraction & $C=V_{p1}- V_{p2}$\\
bubble-point pressure & $R_{s2}\left(P_b\right) = \left[N\left(m B_{1}/B_{g1} +R_{s1}\right)+G_i-G_p\right]/\left(N-N_p\right)$ \\ \bottomrule
\end{tabular}
\caption{Complete set of material balance equations.}
\label{tab: MBE}
\end{table*}
